Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
another pass on RQ3

\Mar{---------------------- I am here}

Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. $33$ of the $260$
faulty versions are cases whose faulty statements decreased in the ranking list due to being a fault of omission case or due to limitations regarding the test design which \ds{} could not handle. Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases that are result of the limitations mentioned before. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
Instead, if $k=10$ is considered the proposed approach returns an improvement of
$6.1$ on the rank mean of all faulty statements.
This $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none. Yet,
if we only consider the faults ($116$) where there was improvement in at least
one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for
$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained
in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which
is significant.

>>>>

If we focus at the $116$\Mar{117?} faults where there was improvement
in at least one of the variants, the mean improvement in the ranking
was 41.1 statements for $k=5$ and 18.7 statements for $k=10$. We
observed an impressive maximum ranking improvement of $3170.5$\Mar{why
  the .5 if this is the maximum case?} statements for $k=5$ and $209$
statements for $k=10$. Such difference is justified by the fact that
entire files are discarded in \combpar{5}, whose statements are
included in the ranking of \combpar{10}. Consequently, the
improvements obtained by the technique will not be as high if slicing
on these additional files is unable to aggressively and safely discard
statements. This also shows that slicing files, in addition to slicing
statements from those files, is very beneficial for fault localization
performance.

\Mar{show distribution...}

In the following, we present statistical analysis to demonstrate that
the distributions of $C$ for each technique are different.
Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. $33$ of the $260$
faulty versions are cases whose faulty statements decreased in the ranking list due to being a fault of omission case or due to limitations regarding the test design which \ds{} could not handle. Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases that are result of the limitations mentioned before. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
Instead, if $k=10$ is considered the proposed approach returns an improvement of
$6.1$ on the rank mean of all faulty statements.
These $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none.
